\texorpdfstring{\ZpL}{ZpL}: a p-adic precision package

### 2018-05-08 ZpL/ZpL.tex
number_of_diffused_digits -> diffused_digits

%\ZpL can count the number of diffused digits.
%\begin{tabular}{rl}
%\cIn
% & {\color{ring}\verb?Z2?}\verb?.precision().?{\color{method}\verb?number_of_diffused_digits?}\verb?()? \\
%\ZpLC
% & \verb?604? \\
%\end{tabular}

@@

The method {\color{method}\verb?number_of_diffused_digits?} computes the number of
diffused digits of precision on a set of variables. Observe:

@@

{\noindent \small
\begin{tabular}{rl}
\cIn   & \verb?L.?{\color{method}\verb?number_of_diffused_digits?}\verb?([x,y])? \\
\cZpLC & \verb?0? \\
\cIn   & \verb?L.?{\color{method}\verb?number_of_diffused_digits?}\verb?([u,v])? \\
\cZpLC & \verb?6? \\
\end{tabular}}

@@

{\noindent \small
\begin{tabular}{rl}
\cIn & \verb?L.?{\color{method}\verb?number_of_diffused_digits?}\verb?(M.?{\color{method}\verb?list?}\verb?())? \\
\cZpLC & \verb?11? \\
\end{tabular}}

>>>>

%\ZpL can count the number of diffused digits.
%\begin{tabular}{rl}
%\cIn
% & {\color{ring}\verb?Z2?}\verb?.precision().?{\color{method}\verb?diffused_digits?}\verb?()? \\
%\ZpLC
% & \verb?604? \\
%\end{tabular}

@@

The method {\color{method}\verb?diffused_digits?} computes the number of
diffused digits of precision on a set of variables. Observe:

@@

{\noindent \small
\begin{tabular}{rl}
\cIn   & \verb?L.?{\color{method}\verb?diffused_digits?}\verb?([x,y])? \\
\cZpLC & \verb?0? \\
\cIn   & \verb?L.?{\color{method}\verb?diffused_digits?}\verb?([u,v])? \\
\cZpLC & \verb?6? \\
\end{tabular}}

@@

{\noindent \small
\begin{tabular}{rl}
\cIn & \verb?L.?{\color{method}\verb?diffused_digits?}\verb?(M.?{\color{method}\verb?list?}\verb?())? \\
\cZpLC & \verb?11? \\
\end{tabular}}
